Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-01-14 paper/zhang-cook-laa-langrene-menendez.Rmd
writing for explore_trace_search()

Figure \ref{fig:toy-search} shows a sample of the plot constructed using `search_better` with different values of the parameter `max_tries`. Comparing the returned index value of each iteration shows that the termination at `max_tries = 25` is not sufficient for `search_better` to explore the parameter space and a value of 500 is preferred over 25 in this context.

```{r toy-search, fig.cap="A comparison of \\code{search\\_better} with different values of the parameter \\code{max\\_tries}. A six-variable dataset \\code{boa6} is used with holes index on a 2D problem. \\code{max\\_tries = 500} allows the optimiser to find better basis with higher index value at iteration six."}
```

>>>>

Figure \ref{fig:toy-search} shows the searches of two different optimisers: `search_better` and `search_better_random`. Both optimisers progress quickly at the first few iterations, take longer to find better basis in the later iterations, and finish off when hitting the maximum number of try, 499 and 999, respectively. Also, the target basis found in each iteration of `search_better` always has an increased index value while this is not the case for `search_better_random`. This explains why in this example, `search_better_random` takes longer to find the final basis, but in more complicated scenarios, the feature of probabilistic acceptance allows a more holistic search of the basis space and is more likely to find the global optimum.

```{r toy-search, fig.cap="A comparison of search by two otimisers: \\code{search\\_better} and \\code{search\\_better\\_random} on a six-variable dataset \\code{boa6} with holes index on a 2D problem. Both optimisers finish when the maximum number of try is reached and attain similar index value in the end. \\code{search\\_better\\_random} takes longer to get to the final basis because it allows for probabilistic acceptance of inferior basis, which is a feature useful for more complex problem."}
```

### 2021-01-14 paper/zhang-cook-laa-langrene-menendez.tex
writing for explore_trace_search()

Figure \ref{fig:toy-search} shows a sample of the plot constructed using
\texttt{search\_better} with different values of the parameter
\texttt{max\_tries}. Comparing the returned index value of each
iteration shows that the termination at \texttt{max\_tries\ =\ 25} is
not sufficient for \texttt{search\_better} to explore the parameter
space and a value of 500 is preferred over 25 in this context.

@@

\caption{A comparison of \code{search\_better} with different values of the parameter \code{max\_tries}. A six-variable dataset \code{boa6} is used with holes index on a 2D problem. \code{max\_tries = 500} allows the optimiser to find better basis with higher index value at iteration six.}\label{fig:toy-search}
\end{figure}
\end{Schunk}

>>>>

Figure \ref{fig:toy-search} shows the searches of two different
optimisers: \texttt{search\_better} and \texttt{search\_better\_random}.
Both optimisers progress quickly at the first few iterations, take
longer to find better basis in the later iterations, and finish off when
hitting the maximum number of try, 499 and 999, respectively. Also, the
target basis found in each iteration of \texttt{search\_better} always
has an increased index value while this is not the case for
\texttt{search\_better\_random}. This explains why in this example,
\texttt{search\_better\_random} takes longer to find the final basis,
but in more complicated scenarios, the feature of probabilistic
acceptance allows a more holistic search of the basis space and is more
likely to find the global optimum.

@@

\caption{A comparison of search by two otimisers: \code{search\_better} and \code{search\_better\_random} on a six-variable dataset \code{boa6} with holes index on a 2D problem. Both optimisers finish when the maximum number of try is reached and attain similar index value in the end. \code{search\_better\_random} takes longer to get to the final basis because it allows for probabilistic acceptance of inferior basis, which is a feature useful for more complex problem.}\label{fig:toy-search}
\end{figure}
\end{Schunk}
